

#Diversity indices
```{r}
library(dplyr)
library(vegan)
library(ggplot2)
library(reshape)
library(betapart)
library(skimr)
library(tibble)

# Full data
MASTER <- read.delim(here::here("DATA/MASTER.csv")) %>% as_tibble()

# Removing useless columns + Removing data of OHU2
#MASTER_8 <- MASTER %>% 
 # dplyr:: select(locality, CAT_sp, PLANT_sp, PAR_sp, guild) %>% 
  # dplyr:: filter(locality != "Ohu2")



# Loading distance matrix
Distance <- read.csv2("DATA/Distance.csv", row.names=1) # loading distance matrix of localities
#Distance <-Distance[!(rownames(Distance) == "Ohu2"), !(colnames(Distance) == "Ohu2")]

# Prepare the distance matrix for a figure
Distance_fig <- read.csv2("DATA/Distance.csv")

distance_2 <- reshape::melt(Distance_fig)   #melt a matrix
#distance_2 <- distance_2[!(distance_2$X == "Ohu2" | distance_2$variable == "Ohu2"), ]

distance_plot <- dplyr::rename (distance_2, Locality_A = X, Locality_B = variable, distance = value)  # rename columns

# data for parasitoids
para_pivot<-  MASTER  %>%
  select(locality, PAR_sp, Par_remove)

para_pivot <- para_pivot %>% 
  filter(Par_remove == "0")

para_pivot2 <- as.matrix(table(para_pivot$locality, para_pivot$PAR_sp))  # dataframe ready for indices
para_pivot2[is.na(para_pivot2)] <- 0 # Replacing NA values with 0
para_pivot_P_A <- para_pivot2
para_pivot_P_A [para_pivot_P_A > 0] <- 1 #converts from abundance to P/A - for Sorensen index only

# Make a dataframe for caterpillars
cat_pivot <-  MASTER %>% 
   select(locality, CAT_sp)

cat_pivot2 <- as.matrix(table(cat_pivot$locality, cat_pivot$CAT_sp))  # dataframe ready for indices
cat_pivot2[is.na(cat_pivot2)] <- 0 # Replacing NA values with 0
cat_pivot_P_A <- cat_pivot2
cat_pivot_P_A [cat_pivot_P_A > 0] <- 1 #converts from abundance to P/A for Sorensen index only
```


```{r Pocty}
skim(MASTER)

family_species <- MASTER %>%
   select(PAR_sp, locality, PLANT_sp)

# Count the number of unique species in each locality
species_locality_count <- family_species %>%
   group_by(locality, PLANT_sp) %>%
   summarise(
      species_count = n_distinct(PAR_sp),  # Count unique species
      abundance = n()  # Count total occurrences (abundance)
   )

# View the result
species_locality_count


family_species_cat <- MASTER %>%
   select(CAT_sp, locality)

# Count the number of unique species in each locality
species_locality_count_cat <- family_species_cat %>%
   group_by(locality) %>%
   summarise(
      species_count = n_distinct(CAT_sp),  # Count unique species
      abundance = n()  # Count total occurrences (abundance)
   )
# View the result
species_locality_count_cat
```

```{r Bray-Curtis, echo=FALSE}
#Bray-Curtis index for parasitoids
BC_par_res <- vegan::vegdist(para_pivot2, method="bray", binary=FALSE, diag=TRUE) %>% as.matrix()
BC_res_par_mantel <- vegan::mantel(BC_par_res, Distance , method="spear"); BC_res_par_mantel


####preparation for a figure - Bray-Curtis
Bray_C_parasitoids <- reshape::melt(BC_par_res)
Bray_C_figure_par <- dplyr::rename (Bray_C_parasitoids, Locality_A = Var1, Locality_B = Var2, hodnota = value) # rename columns
Bray_C_figure_par <- Bray_C_figure_par %>%
  add_column(guild = "Parasitoids")
par_fig_table_BC <-merge(Bray_C_figure_par, distance_plot, by=c("Locality_A", "Locality_B")) %>% 
  filter (hodnota > 0)

# 
BC_par_inter <- lm(hodnota ~ distance, data = par_fig_table_BC) # 0.679025     0.000375
anova(BC_par_inter)
BC_par_inter$coefficients


# coefficients
BC_lm_par <- lm(hodnota~distance, data = par_fig_table_BC)
BC_lm_par

par_BC_mean <- summarise(par_fig_table_BC,
                     mean_BC = mean(hodnota),
                     sd_BC= sd(hodnota)) 
par_BC_mean


mantel_result_Par_BC <- data.frame(
  index ="Bray-Curtis",
  Community = "Parasitoids",
  mean = round(par_BC_mean$mean_BC,3),
  sd = round(par_BC_mean$sd_BC,3),
  test = "Mantel",
  statistic = round (BC_res_par_mantel$statistic,3),
  p.value = round(BC_res_par_mantel$signif,3),    Dataset = "Full",
  stringsAsFactors = FALSE
)
print(mantel_result_Par_BC )


# Bray-Curtis index for caterpillars

BC_cat_res<- vegdist(cat_pivot2, method="bray", binary=FALSE, diag=TRUE) %>%  as.matrix()
BC_cat_res_mantel <- mantel(BC_cat_res, Distance , method="spear"); BC_cat_res_mantel

####preparation for a figure
Bray_C_Caterpillars <- melt(BC_cat_res)
Bray_C_figure_cat <- dplyr::rename (Bray_C_Caterpillars, Locality_A = Var1, Locality_B = Var2, hodnota = value)
Bray_C_figure_cat <- Bray_C_figure_cat %>%
  add_column(guild = "Caterpillars")

Cat_fig_table_BC <-merge(Bray_C_figure_cat, distance_plot, by=c("Locality_A", "Locality_B")) %>% 
  filter (hodnota > 0)


cat_bc_mean <- summarise(Cat_fig_table_BC,
                     mean = mean(hodnota),
                     sd = sd(hodnota)) 
cat_bc_mean

BC_lm_cat <- lm(hodnota~distance, data = Cat_fig_table_BC)
BC_lm_cat # 0.5019007    0.0003242


mantel_result_cat_BC <- data.frame(
  index ="Bray-Curtis",
  Community = "Caterpillars",
  mean = round(cat_bc_mean$mean,3),
  sd = round(cat_bc_mean$sd,3),
  test = "Mantel",
  statistic = round (BC_cat_res_mantel$statistic,3),
  p.value = round(BC_cat_res_mantel$signif,3),    Dataset = "Full",
  stringsAsFactors = FALSE
)
print(mantel_result_cat_BC)
```

```{r Chao-Sorensen, echo=FALSE}
# Chao-Sorensen index for parasitoids
CS_par_res<- CommEcol:: dis.chao(para_pivot2, index="sorensen", version="rare", freq=NULL) %>%  as.matrix()
CS_par_res_mantel <- mantel(CS_par_res, Distance , method="spear"); CS_par_res_mantel

####preparation for a figure - Chao-Sorensen - Parasitoids
Chao_Sor_parasitoids <- melt(CS_par_res)
Chao_Sor_figure_par <- dplyr::rename (Chao_Sor_parasitoids, Locality_A = Var1, Locality_B = Var2, hodnota = value)
Chao_Sor_figure_par <- Chao_Sor_figure_par %>%
  add_column(guild = "Parasitoids")
par_fig_table_CS <-merge(Chao_Sor_figure_par, distance_plot, by=c("Locality_A", "Locality_B")) %>% 
  filter (hodnota > 0)

par_CS_mean <- summarise(par_fig_table_CS,
                     mean_CS = mean(hodnota),
                     sd_CS= sd(hodnota)) 
par_CS_mean 

CS_lm_par <- lm(hodnota~distance, data = par_fig_table_CS)
CS_lm_par


mantel_result_par_CS <- data.frame(
  index ="Chao-Sorensen",
  Community = "Parasitoids",
  mean = round(par_CS_mean$mean,3),
  sd = round(par_CS_mean$sd,3),
  test = "Mantel",
  statistic = round (CS_par_res_mantel$statistic,3),
  p.value = round(CS_par_res_mantel$signif,3),    Dataset = "Full",
  stringsAsFactors = FALSE
)
print(mantel_result_par_CS)



# Chao-Sorensen index for caterpillars
CS_cat_res<- CommEcol::dis.chao(cat_pivot2, index="sorensen", version="rare", freq=NULL) %>%  as.matrix()
CS_cat_res_mantel <- mantel(CS_cat_res, Distance , method="spear"); CS_cat_res_mantel

####preparation for a figure
Chao_Sor_Caterpillars <- melt(CS_cat_res)
Chao_Sor_figure_cat <- dplyr::rename (Chao_Sor_Caterpillars, Locality_A = Var1, Locality_B = Var2, hodnota = value)
Chao_Sor_figure_cat <- Chao_Sor_figure_cat %>%
  add_column(guild = "Caterpillars")
Cat_fig_table_CS <-merge(Chao_Sor_figure_cat, distance_plot, by=c("Locality_A", "Locality_B")) %>% 
  filter (hodnota > 0)


cat_CS_mean <- summarise(Cat_fig_table_CS,
                     mean_sor = mean(hodnota),
                     sd_sor = sd(hodnota)) 
cat_CS_mean
CS_lm_cat <- lm(hodnota~distance, data = Cat_fig_table_CS)
CS_lm_cat

mantel_result_cat_CS <- data.frame(
  index ="Chao-Sorensen",
  Community = "Caterpillars",
  mean = round(cat_CS_mean$mean,3),
  sd = round(cat_CS_mean$sd,3),
  test = "Mantel",
  statistic = round (CS_cat_res_mantel$statistic,3),
  p.value = round(CS_cat_res_mantel$signif,3),    Dataset = "Full",
  stringsAsFactors = FALSE
)
print(mantel_result_cat_CS)
```

```{r Sorensen, echo=FALSE}
#Sorensen index 

# Sorensen index for parasitoids
sorensen_par<-beta.pair(para_pivot_P_A)#calculate Sorensen dissimilarity
sorensen_par_others<-beta.pair(para_pivot_P_A)
sorensen_par<-(as.matrix(sorensen_par$beta.sor)) #pick sorensen index
sor_mantel_par <- mantel(sorensen_par, Distance, method="spear"); sor_mantel_par #Mantel test for parasitoids

####preparation for a figure - Sorensen - Parasitoids
Sorensen_parasitoids <- melt(sorensen_par)
Sorensen_figure <- dplyr:: rename (Sorensen_parasitoids, Locality_A = Var1, Locality_B = Var2, hodnota = value)
Sorensen_figure <- Sorensen_figure %>%
  add_column(guild = "Parasitoids")
par_fig_table_sor <-merge(Sorensen_figure, distance_plot, by=c("Locality_A", "Locality_B")) %>% 
  filter (hodnota > 0)

par_SOR_mean <- summarise(par_fig_table_sor,
                     mean_sor = mean(hodnota),
                     sd_sor = sd(hodnota)) 
par_SOR_mean

SOR_lm_par <- lm(hodnota~distance, data = par_fig_table_sor)
SOR_lm_par

mantel_result_par_SOR <- data.frame(
  index ="Sorensen",
  Community = "Parasitoids",
  mean = round(par_SOR_mean$mean,3),
  sd = round(par_SOR_mean$sd,3),
  test = "Mantel",
  statistic = round (sor_mantel_par$statistic,3),
  p.value = round(sor_mantel_par$signif,3),  Dataset = "Full",
  stringsAsFactors = FALSE
)
print(mantel_result_par_SOR)


# Sorensen index for caterpillars
sorensen_cat<-beta.pair(cat_pivot_P_A)      #calculate Sorensen dissimilarity
sorensen_cat_others<-beta.pair(cat_pivot_P_A)
sorensen_cat<-(as.matrix(sorensen_cat$beta.sor)) #pick sorensen index
sor_mantel_cat <- mantel(sorensen_cat, Distance, method="spear"); sor_mantel_cat #Mantel test for caterpillars

####preparation for a figure
Sorensen_caterpillars <- melt(sorensen_cat)
Sorensen_figure <- dplyr:: rename (Sorensen_caterpillars, Locality_A = Var1, Locality_B = Var2, hodnota = value)
Sorensen_figure <- Sorensen_figure %>%
  add_column(guild = "Caterpillars")
cat_fig_table_sor <-merge(Sorensen_figure, distance_plot, by=c("Locality_A", "Locality_B")) %>% 
  filter (hodnota > 0)

cat_SOR_mean <- summarise(cat_fig_table_sor,
                     mean_sor = mean(hodnota),
                     sd_sor = sd(hodnota)) 
cat_SOR_mean


SOR_lm_cat <- lm(hodnota~distance, data = cat_fig_table_sor)
SOR_lm_cat

mantel_result_cat_SOR <- data.frame(
  index ="Sorensen",
  Community = "Caterpillars",
  mean = round(cat_SOR_mean$mean,3),
  sd = round(cat_SOR_mean$sd,3),
  test = "Mantel",
  statistic = round (sor_mantel_cat$statistic,3),
  p.value = round(sor_mantel_cat$signif,3),    
  Dataset = "Full",
  stringsAsFactors = FALSE
)
print(mantel_result_cat_SOR)

```

Summary of Indices
```{r}
# Combine all tables into one
all_mantel_results <- rbind(mantel_result_cat_SOR, mantel_result_par_SOR,mantel_result_cat_CS, mantel_result_par_CS, mantel_result_cat_BC, mantel_result_Par_BC)

# Print the merged table# Print the merged tablemantel_result_Par_BC
print(all_mantel_results)

all_mantel_results$Dataset <- "Full"

```

# Subsampling
```{r SOR - Subsampling, echo=FALSE}
library(tidyr)
library(purrr)
MASTER <- read_excel("DATA/MASTER.xlsx") %>% as_tibble() # loading the master file with all data available (detailed info with old sp_code etc check Master_2023 file)
Distance <- read.csv2("DATA/Distance.csv", row.names=1) # loading distance matrix of

data_testing <- MASTER %>% 
  filter(remove_cat == "0") %>% 
  select(locality,CAT_sp, PAR_sp, guild, PLANT_sp)



# calculate the total abundance of parasitoids in each plot
n_par_specimens_in_site <-
  data_testing %>% 
  filter(guild == "PAR") %>%
  drop_na() %>% 
  group_by(locality) %>% 
  summarise(
    .groups= "keep",
    N= n()) %>% 
  ungroup()

# pre-allocate tibble with all sites 
site_tibble <-  
  MASTER %>% 
  group_by(locality) %>% 
  summarise(.groups = "keep")

#----------------------------------------------------------#
# 2.2 Function for subsampling -----
#----------------------------------------------------------#

set.seed(1234)

n_rand <-  999

# pre-alocate space

res_list <- vector("list", length = n_rand)

for (i in 1:n_rand) {
  
  #print(i)
  
  cat_randomly_resampled  <- 
    as.list(site_tibble$locality) %>% 
    purrr::map_df(
      .x = .,
      .f = function(x){
        
        N_para <-
          n_par_specimens_in_site %>% 
          filter(locality == x) %>% 
          dplyr::select(N) %>% 
          pluck(1)
        
        res <-
          MASTER %>% 
          filter(locality == x) %>% 
          sample_n(., size = N_para)
        
        return(res)
      }
    ) %>% 
    bind_rows()
  
  
  #----------------------------------------------------------#
  # 2.3 Saving results and count mean for the data -----
  #----------------------------------------------------------#
  
  df <- 
    cat_randomly_resampled %>% 
    dplyr::select(locality, CAT_sp) %>%
    group_by(locality, CAT_sp) %>% 
    summarise(
      .groups = "keep",
      N = n()) %>% 
    ungroup() %>% 
    pivot_wider(names_from = CAT_sp, values_from = N) %>% 
    replace(is.na(.), 0) %>% 
    column_to_rownames(var = "locality")
  
  df_pres <- df
  
  df_pres[df_pres>1]<-1
  
  #----------------------------------------------------------#
  # 2.4 Sorensen comparison-----
  #----------------------------------------------------------#
 
  
sorensen_dis <- beta.pair(df_pres)   
Sor_res <- (as.matrix(sorensen_dis$beta.sor))
   
    
  
  
  res_list[[i]] <-Sor_res
  
}

#  calculate a mean
Y <- do.call(cbind, res_list)
Y <- array(Y, dim = c(dim(res_list[[1]]), length(res_list)))

Sor_res_mean <-
  apply(Y, c(1, 2), mean, na.rm = TRUE)

rownames(Sor_res_mean) <- c("Elem", "Morox", "Niksek", "Ohu1", "Ohu2", "Utai", "Wamangu", "Wanang","Yapsiei")
colnames(Sor_res_mean) <- c("Elem", "Morox", "Niksek", "Ohu1", "Ohu2", "Utai", "Wamangu", "Wanang","Yapsiei")

# calculate a mean of the results
Sor_mean_sub<-melt(Sor_res_mean)
Sor_mean_sub<- summarise(Sor_mean_sub,
                     mean_Sor = mean(value),
                     sd_Sor = sd(value))
Sor_mean_sub



#----------------------------------------------------------#
# 2.5 Mantel test-----
#----------------------------------------------------------#
library(vegan)
# Distance between localities


res_mantel_sor_sub <-
  mantel(Sor_res_mean, Distance , method="spear")


Sorensen_para_sub<- melt(Sor_res_mean)
Sorensen_figure_sub <- dplyr::rename (Sorensen_para_sub, Locality_A = Var1, Locality_B = Var2, hodnota = value)
Sorensen_figure_sub  <- Sorensen_figure_sub  %>%
  add_column(guild = "Caterpillars-subsampled")
Sorensen_fig_subsampled <-merge(Sorensen_figure_sub, distance_plot, by=c("Locality_A", "Locality_B")) %>% 
  filter (hodnota > 0)


SOR_lm_hous <- lm(hodnota~distance, data = Sorensen_fig_subsampled)
SOR_lm_hous

cat_SOR_sub_mean <- summarise(Sorensen_fig_subsampled,
                     mean_sor = mean(hodnota),
                     sd_sor = sd(hodnota)) 
cat_SOR_sub_mean

mantel_result_cat_SOR_sub <- data.frame(
  index ="Sorensen",
  Community = "Caterpillars-subsampled",
  mean = round(cat_SOR_sub_mean$mean,3),
  sd = round(cat_SOR_sub_mean$sd,3),
  test = "Mantel",
  statistic = round (res_mantel_sor_sub$statistic,3),
  p.value = round(res_mantel_sor_sub$signif,3),    Dataset = "Full",
  stringsAsFactors = FALSE
)
print(mantel_result_cat_SOR_sub)


```

```{r BC - subsampling}


MASTER <- read_excel("DATA/MASTER.xlsx") %>% as_tibble() # loading the master file with all data available (detailed info with old sp_code etc check Master_2023 file)
Distance <- read.csv2("DATA/Distance.csv", row.names=1) # loading distance matrix of

data_testing <- MASTER %>% 
  filter(remove_cat == "0") %>% 
  select(locality,CAT_sp, PAR_sp, guild, PLANT_sp)



# calculate the total abundance of parasitoids in each plot
n_par_specimens_in_site <-
  data_testing %>% 
  filter(guild == "PAR") %>%
  drop_na() %>% 
  group_by(locality) %>% 
  summarise(
    .groups= "keep",
    N= n()) %>% 
  ungroup()

# pre-allocate tibble with all sites 
site_tibble <-  
  data_testing %>% 
  group_by(locality) %>% 
  summarise(.groups = "keep")




#----------------------------------------------------------#
# 2.2 Function for subsampling -----
#----------------------------------------------------------#

set.seed(1234)

n_rand <-  1000


res_list <- vector("list", length = n_rand)

for (i in 1:n_rand) {
 
  #print(i)
  
   cat_randomly_resampled  <- 
    as.list(site_tibble$locality) %>% 
    purrr::map_df(
      .x = .,
      .f = function(x){
        
        N_para <-
          n_par_specimens_in_site %>% 
          filter(locality == x) %>% 
          dplyr::select(N) %>% 
          pluck(1)
        
        res <-
          data_testing %>% 
          filter(locality == x) %>% 
          sample_n(., size = N_para)
        
        return(res)
      }
    ) %>% 
    bind_rows()
   
  df <- 
    cat_randomly_resampled %>% 
    dplyr::select(locality, CAT_sp) %>%
    group_by(locality, CAT_sp) %>% 
    summarise(
      .groups = "keep",
      N = n()) %>% 
    ungroup() %>% 
    pivot_wider(names_from = CAT_sp, values_from = N) %>% 
    replace(is.na(.), 0) %>% 
    column_to_rownames(var = "locality")
  
  
    
#----------------------------------------------------------#
# 2.4 Bray_curtis comparison-----
#----------------------------------------------------------#


BC_res <- vegdist(df, method="bray", binary=FALSE, diag=TRUE) %>% 
  as.matrix()


res_list[[i]] <- BC_res

}

#  calculate a mean
Y <- do.call(cbind, res_list)
Y <- array(Y, dim = c(dim(res_list[[1]]), length(res_list)))

BC_res_mean <-
  apply(Y, c(1, 2), mean, na.rm = TRUE)


rownames(BC_res_mean) <- c("Elem", "Morox", "Niksek", "Ohu1", "Ohu2", "Utai", "Wamangu", "Wanang","Yapsiei")
colnames(BC_res_mean) <- c("Elem", "Morox", "Niksek", "Ohu1", "Ohu2", "Utai", "Wamangu", "Wanang","Yapsiei")






# calculate a mean of the results
BC_melt<-melt(BC_res_mean)
BC_melt <- dplyr::rename (BC_melt, Locality_A = X1, Locality_B = X2, hodnota = value)

BC_melt_subsampling <- BC_melt %>% 
  add_column(guild = "Caterpillars_subsampled")
BC_melt_subsampling_fig <-merge(BC_melt_subsampling, distance_plot, by=c("Locality_A", "Locality_B")) %>% 
  filter (hodnota > 0)



BC_mean_sub <- summarise(BC_melt,
                     mean_BC = mean(value),
                     sd_BC = sd(value))


mantel_result_cat_BC_subsampled <- data.frame(
  index ="Bray-Curtis",
  Community = "Caterpillars - subsampled",
  mean = round(BC_mean_sub$mean,3),
  sd = round(BC_mean_sub$sd,3),
  test = "Mantel",
  statistic = round (BC_cat_res_mantel$statistic,3),
  p.value = round(BC_cat_res_mantel$signif,3),
  stringsAsFactors = FALSE
)
print(mantel_result_cat_BC_subsampled)
#BC_mean


```


```{r CS - subsampling, echo=FALSE}
# calculate the total abundance of parasitoids in each plot
n_par_specimens_in_site <-
  MASTER %>% 
  filter(guild == "PAR") %>%
  drop_na() %>% 
  group_by(locality) %>% 
  summarise(
    .groups= "keep",
    N= n()) %>% 
  ungroup()

# pre-allocate tibble with all sites 
site_tibble <-  
  MASTER %>% 
  group_by(locality) %>% 
  summarise(.groups = "keep")


#----------------------------------------------------------#
# 2.2 Function for subsampling -----
#----------------------------------------------------------#

set.seed(1234)

n_rand <-  1000

# pre-alocate space

res_list <- vector("list", length = n_rand)

for (i in 1:n_rand) {
 
  #print(i)
  
   cat_randomly_resampled  <- 
    as.list(site_tibble$locality) %>% 
    purrr::map_df(
      .x = .,
      .f = function(x){
        
        N_para <-
          n_par_specimens_in_site %>% 
          filter(locality == x) %>% 
          dplyr::select(N) %>% 
          pluck(1)
        
        res <-
          MASTER %>% 
          filter(locality == x) %>% 
          sample_n(., size = N_para)
        
        return(res)
      }
    ) %>% 
    bind_rows()
  
    
  #----------------------------------------------------------#
  # 2.3 Saving results and count mean for the data -----
  #----------------------------------------------------------#
  
  df <- 
    cat_randomly_resampled %>% 
    dplyr::select(locality, CAT_sp) %>%
    group_by(locality, CAT_sp) %>% 
    summarise(
      .groups = "keep",
      N = n()) %>% 
    ungroup() %>% 
    pivot_wider(names_from = CAT_sp, values_from = N) %>% 
    replace(is.na(.), 0) %>% 
    column_to_rownames(var = "locality")
  
  #----------------------------------------------------------#
  # 2.4 Chao_Sorensen comparison-----
  #----------------------------------------------------------#
 
  
  Chao_Sor_res <- 
    CommEcol::dis.chao(df, index="sorensen", version="rare", freq=NULL) %>% 
    as.matrix()
  
  
  res_list[[i]] <- Chao_Sor_res
  
}

#  calculate a mean
Y <- do.call(cbind, res_list)
Y <- array(Y, dim = c(dim(res_list[[1]]), length(res_list)))

Chao_Sor_res_mean <-
apply(Y, c(1, 2), mean, na.rm = TRUE)


rownames(Chao_Sor_res_mean) <- c("Elem", "Morox", "Niksek", "Ohu1", "Ohu2", "Utai", "Wamangu", "Wanang","Yapsiei")
colnames(Chao_Sor_res_mean) <- c("Elem", "Morox", "Niksek", "Ohu1", "Ohu2", "Utai", "Wamangu", "Wanang","Yapsiei")


# calculate a mean of the results
CS_melt_sub<-melt(Chao_Sor_res_mean)
CS_mean_sub <- summarise(CS_melt_sub,
                      mean_CS = mean(value),
                      sd_CS = sd(value))
#----------------------------------------------------------#
# 2.5 Mantel test-----
#----------------------------------------------------------#
library(vegan)
# Distance between localities
Distance2 <- 
  read.csv2(
    here::here("~/ownCloud/000_/000_R_stat/Beta_diversity/data/input/Distance22.csv"), row.names=1)

res_mantel <-
mantel(Chao_Sor_res_mean, Distance2 , method="spear")

saveRDS(
  Chao_Sor_res_mean,
  here::here("~/ownCloud/000_/000_R_stat/ParaDiv_2023/output/Chao_Sor_res_mean.rds")
)

saveRDS(
  res_mantel,
  here::here("~/ownCloud/000_/000_R_stat/ParaDiv_2023/output/mantel_result.rds")
)


CS_subsampled_res_cat <- rename (CS_melt, Locality_A = Var1, Locality_B = Var2, hodnota = value)
CS_subsampled_figure_cat <- CS_subsampled_res_cat %>%
  add_column(guild = "Caterpillars-subsampled") %>% 
  filter (hodnota > 0)
  
CS_subsampled_figure_cat<- merge(CS_subsampled_figure_cat, distance_plot, by=c("Locality_A", "Locality_B"))


CS_lm_hou <- lm(hodnota~distance, data = CS_subsampled_figure_cat)
CS_lm_hou





mantel_result_cat_CS_sub <- data.frame(
  index ="Chao-Sorensen",
  Community = "Caterpillars-subsampled",
  mean = round(CS_mean_sub$mean,3),
  sd = round(CS_mean_sub$sd,3),
  test = "Mantel",
  statistic = round (res_mantel_CS_sub$statistic,3),
  p.value = round(res_mantel_CS_sub$signif,3),    Dataset = "Full",
  stringsAsFactors = FALSE
)
print(mantel_result_cat_CS_sub)

```


Tabulka
```{r Tabulka}
# Combine all tables into one - main WITHOUT subsampling
all_mantel_results <- rbind(mantel_result_cat_SOR, mantel_result_par_SOR,mantel_result_cat_CS, mantel_result_par_CS, mantel_result_cat_BC, mantel_result_Par_BC)
# Print the merged table# Print the merged tablemantel_result_Par_BC
print(all_mantel_results)
```


# Rarity and common species of parasitoids
```{r}
common_par <- MASTER %>%
  filter(rarity == "0") %>%
  select (locality, PAR_sp)

rare_par <- MASTER %>%
  filter(rarity == "1") %>%
  select (locality, PAR_sp)

para_pivot2c <- as.matrix(table(common_par$locality, common_par$PAR_sp))  # dataframe ready for indices
para_pivot2c[is.na(para_pivot2c)] <- 0 # Replacing NA values with 0
para_pivot_P_Ac <- para_pivot2c
para_pivot_P_Ac [para_pivot_P_Ac > 0] <- 1 #converts from abundance to P/A - for Sorensen index only

#Bray-Curtis index for parasitoids
BC_par_resc <- vegdist(para_pivot2c, method="bray", binary=FALSE, diag=TRUE) %>% as.matrix()
BC_res_par_mantelc <- mantel(BC_par_resc, Distance , method="spear"); BC_res_par_mantel



####preparation for a figure - Bray-Curtis
Bray_C_parasitoidsc <- melt(BC_par_resc)
Bray_C_figure_parc <- Bray_C_parasitoidsc %>%
  add_column(guild = "Rare")
Bray_C_figure_parc <- Bray_C_figure_parc %>%
  dplyr::rename(Locality_A = Var1, Locality_B = Var2, hodnota=value)

par_fig_table_BCc <-merge(Bray_C_figure_parc, distance_plot, by=c("Locality_A", "Locality_B")) %>% 
  filter (hodnota > 0)



################ Tady

para_pivot2ra <- as.matrix(table(rare_par$locality, rare_par$PAR_sp))  # dataframe ready for indices
para_pivot2ra[is.na(para_pivot2ra)] <- 0 # Replacing NA values with 0
para_pivot_P_Ara <- para_pivot2ra
para_pivot_P_Ara [para_pivot_P_Ara > 0] <- 1 #converts from abundance to P/A - for Sorensen index only

#Bray-Curtis index for parasitoids
BC_par_resra <- vegdist(para_pivot2ra, method="bray", binary=FALSE, diag=TRUE) %>% as.matrix()
BC_res_par_mantelra <- mantel(BC_par_resra, Distance , method="spear"); BC_res_par_mantel



####preparation for a figure - Bray-Curtis
Bray_C_parasitoidsra <- melt(BC_par_resra)
Bray_C_figure_parra <- Bray_C_parasitoidsra %>%
  add_column(guild = "rare")
Bray_C_figure_parra <- Bray_C_figure_parra %>%
  dplyr::rename(Locality_A = X1, Locality_B = X2, hodnota=value)

par_fig_table_BCra <-merge(Bray_C_figure_parra, distance_plot, by=c("Locality_A", "Locality_B")) %>% 
  filter (hodnota > 0)

bray_common_rare <- rbind(par_fig_table_BCra,par_fig_table_BCc)



ggplot(bray_common_rare, aes(y = hodnota, 
                 color = guild, shape = guild, linetype = guild)) +
  geom_boxplot() +  # Adjust size as needed
  coord_cartesian(ylim = c(0, 1)) +
  theme_minimal() +
    theme_classic(base_size = 20)





```


```

# Tabulka celistvá
```{r Tabulka}
# Tabulka with rarity of parasitoids
tabulka_rarity <- rbind(mantel_result_Par_BC_common_plants, mantel_result_Par_BC_rare_common_plants, mantel_result_Par_BC_common_common_plants,
mantel_result_Par_CS_common_plants_all, mantel_result_Par_CS_rare_common_plants, mantel_result_Par_CS_common_common_plants,
mantel_result_Par_sor_common_common_plants_all,mantel_result_Par_sor_rare_common_plants,  mantel_result_Par_sor_common_common_plants) ;tabulka_rarity


# Tabulka without OHU2
Mantel_table_8 <- rbind(all_mantel_results_8, all_mantel_results_8_sub )


Mantel_table <- rbind(all_mantel_results, Mantel_table_8, tabulka_rarity )

# Round numeric columns to three decimal places
Mantel_table <- Mantel_table %>%
  dplyr::mutate(across(c(mean, sd, test_statistic, p.value), ~ round(., 3)))

# Format the table using gt
Mantel_gt <-Mantel_table %>%
  gt() %>%
  tab_header(
    title = "Mantel test results",
  ) %>%
  cols_label(
    index = "Index",
    Community = "Community",
    mean = "Mean",
    sd = "SD",
    statistic = "Test Statistic",
    p.value = "P-Value",
    Dataset = "Dataset"
  ) %>%
  tab_style(
    style = list(cell_text(align = "center")),
    locations = cells_body()
  )

gtsave(Mantel_gt, "Mantel_Test_Results.png")

library(openxlsx)

# Save the Mantel_table as an Excel file
write.xlsx(Mantel_table, "Mantel_Test_Results.xlsx")


```
